---
title: "101CHW3"
author: "JING LI"
date: "4/20/2017"
output:
  pdf_document: default
  html_document: default
---

2.4.8

a) no need to report an ???answer??? here
```{r}
college <- read.csv("College.csv")
View(college)
```

b) no need to report an answer here, either
```{r}
rownames(college) <- college[,1] 

college=college[,-1]

```

c) Skip parts i-vi. Instead, just do this:

Write down two ???statistical questions??? that you feel would be interesting to people. Answer these questions using both graphs (made using ggplot2) and  numerical summaries.
Q1. Do private schools have higher instrctional expenditure than public schools?

```{r}
library(ggplot2)
p1 <- ggplot(college, aes(Private, Expend)) + geom_boxplot()
p1
m1.aov <- aov(Expend~Private, data = college)
summary(m1.aov)
```
From the boxplot and the numerical summery(due to small p-value), we conclude that in general, students in private schools have higher instructional expenditures than students in public schools do.

Q2. Do private schools have higher Student/faculty ratio than public schools?

```{r}
p2 <- ggplot(college, aes(Private, S.F.Ratio)) + geom_boxplot()
p2
m2.aov <- aov(S.F.Ratio~Private, data = college)
summary(m2.aov)
```
In this case, both methods suggest that there is strong evidence indicating higher student/faculty ratio in public schools. This conclusion make sense because public schools usually have more students and less faculty members.


4.7.1

Using a little bit of algebra, prove that (4.2) is equivalent to (4.3). In other words, the logistic function representation and logit representation for the logistic regression model are equivalent.

$p(X) = \frac {e^{\beta_0 + \beta_1X}} {1 +e^{\beta_0 + \beta_1X}}$  

if and only if  

$e^{\beta_0 + \beta_1X}(1-p(X)) = p(X)$

Hence,

$\frac {p(X)} {1-p(X)} = e^{\beta_0 + \beta_1X}$  

4.7.4
a.  

If 0.05<x<0.95, we use the interval [x???0.05,x+0.05].  
If x<0.05, we will use the interval [0,x+0.05]
If x>0.95, we will use the interval [x+0.05,1]
So the average is:  

$\int_{0.05}^{0.95}10dx + \int_{0.05}^0 (100x+5)dx + \int_{0.95}^1(105-100x)dx = 9+0.375+0.375 = 9.75$

So, on average, the fraction we use to make the prediction is 9.75%.

b.
If we assume X1 and X2 are independant, the fraction we use to make the prediction is 9.75%??9.75%=0.950625%.  

c.
With the assumptions under a and b, the fraction we use to make the prediction is 9.75%^100, which is close to 0.

4.7.6
a.
X1=40, X2=3.5,  
$\hat{p}(X) = \frac{e^{-6+0.05X_1+X_2}}{1+e^{-6+0.05X_1+X_2}} =  0.3775$  

b.
X2=3.5,
$\frac{e^{-6+0.05X_1+3.5}}{1+e^{-6+0.05X_1+3.5}} = 0.5 $
$ e^{-6+0.05X_1+3.5} = 1$
take log on both sides, we get
$ -6+0.05X_1+3.5 = log(1) $
$ 0.05X_1 = 2.5 $
$ X_1 = 2.5/0.05 = 50 $


4.7.10a-e,g,h

a.
```{r}
library(ISLR)
summary(Weekly)
```

```{r}
cor(Weekly[,-9])
```
```{r}
attach(Weekly)
plot(Weekly)
```

From the correlation matrix and the matrix plot, we can see that the variables Year and Volume are highly correlated.

b.  
```{r}
m3.log <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, family = binomial)
summary(m3.log)
```

Lag2 appears to be significant with a small p-value. 

c.
```{r}
prob <- predict(m3.log, type = "response")
pred <- rep("Down", length(prob))
pred[prob > 0.5] <- "Up"
table(pred, Direction)

```

The percentage of correct predictions on the training data is (54+557)/1089 = 56.1065197%. When the market goes up, the model is 557/(48+557) = 92.0661157% correct.However, when the market goes down, the model is 54/(54+430) = 11.1570248% correct.

d.  
```{r}
train <- (Year < 2009)
WeeklyBefore2009 <- Weekly[!train, ]
DirectionBefore2009 <- Direction[!train]
m4.log <- glm(Direction ~ Lag2, data = Weekly, family = binomial, subset = train)
summary(m4.log)
```

```{r}
prob_d <- predict(m4.log, WeeklyBefore2009, type = "response")
pred_d <- rep("Down", length(prob_d))
pred_d[prob_d > 0.5] <- "Up"
table(pred_d, DirectionBefore2009)
```

The percentage of correct predictions on the training data is (9+56)/104 = 62.5%. When the market goes up, the model is 56/(56+5) = 91.8032787%% correct.However, when the market goes down, the model is 9/(9+34) = 20.9302326% correct.  
e. 
```{r}
library(MASS)
lda <- lda(Direction ~ Lag2, data = Weekly, subset = train)
lda
```
```{r}
pred_lda <- predict(lda, WeeklyBefore2009)
table(pred_lda$class, DirectionBefore2009)
```

The result is the same as part d.

g.
```{r}
library(class)
train_X <- as.matrix(Lag2[train])
test_X <- as.matrix(Lag2[!train])
train_Direction <- Direction[train]
set.seed(123)
pred_knn <- knn(train_X, test_X, train_Direction, k = 1)
table(pred_knn, DirectionBefore2009)
```

The percentage of correct predictions on the training data is (21+32)/104 = 50.961538%. When the market goes up, the model is 32/(29+32) = 52.459016% correct.However, when the market goes down, the model is 21/(21+22) = 48.837209% correct.  


h. 
Here, logistic regression model provides the best results in this data.
