---
title: "101CHW8"
author: "JING LI"
date: "5/25/2017"
output: pdf_document
---

1. 
a) 
Accurate means that estimator is centered around the true value, while precise means that our prediction is clustered, close to each other.

b) 
Yes the estimator is biased, because Xbar will never converge to the true population mean when n goes to infinity. 


c) 
```{r}
xbar <- c()
xbarplus1 <- c()
for (i in 1:1000) {
xbar[i] <- mean(rnorm(100,100,10))
  xbarplus1[i] <- xbar[i] + 1
}
mean(xbarplus1)
hist(xbarplus1)
```

According to the graph, the prediction mean is centered at 101, while the true population mean is 100.

d) 
```{r}
SE <- sqrt(var(xbar)/length(xbar)) 
SEplus1 <- sqrt(var(xbarplus1)/length(xbarplus1)) 
SE
SEplus1
```

The variances are exactly the same, since var(x)=var(x+1). The center is shifted, but the variance will not change.

d)
```{r}
xbar <- c()
xbarplus1 <- c()
for (i in 1:1000) {
xbar[i] <- mean(rnorm(1000,100,10))
  xbarplus1[i] <- xbar[i] + 1
}
mean(xbarplus1)
hist(xbarplus1)
```


e) 
```{r}
SE <- sqrt(var(xbar)/length(xbar)) 
SEplus1 <- sqrt(var(xbarplus1)/length(xbarplus1)) 
SE
SEplus1
```
Standard error is smaller for 1000 simulations, i.e. the precision increased.

f) Suppose you are fitting a model with a data set of size n and you estimate the testing MSE.  Then, you get twice as much data. What do you think will change in the estimate of the testing MSE?

Precision can be different, but accuracy will not change.

2) 

```{r}
gini=function(m1){
  return(2*(m1*(1-m1)))
}

ent=function(m1){
  m2=1-m1
  return(-((m1*log(m1))+(m2*log(m2))))
}

classerr=function(m1){
  m2=1-m1
  return(1-max(m1,m2))
  #return(min((1-m1),m1))
  #return(m1)
}

err=seq(0,1,by=0.01)
c.err=sapply(err,classerr)
g=sapply(err,gini)
e=sapply(err,ent)
d=data.frame(Gini.Index=g,Cross.Entropy=e)
plot(err,c.err,type='l',col="red",xlab="m1",ylim=c(0,0.8),ylab="value")
matlines(err,d,col=c("green","blue"))


```


3) 
```{r} 
library(readr)
births <- read_csv("~/Downloads/better2000births.csv")
births$Premie <- as.factor(births$Premie)
```

a)
```{r}
set.seed(1234)
i.train <- sample(nrow(births),1000, replace = FALSE) 
train <- births[i.train,]
test <- births[-i.train,]
library(tree)
Tree <- tree(Premie~., data = train)
Pred <- predict(Tree, newdata = test,type = "class") 
summary(Tree)
testerror <- sum(test$Premie != Pred)/nrow(test)
testerror
```


b)
```{r}
cv.train <- cv.tree(Tree, FUN = prune.misclass)
cv.train
plot(cv.train$dev ~ cv.train$size)
plot(cv.train$k ~ cv.train$size)
Fit <-prune.misclass(Tree, best = 2)
plot(Fit)
summary(Fit)
```

c) 
Babies weigh less than 87.5 is likely to be premies. Causation cannot be drawn from the pruned model.


d) 
```{r}
pred <- predict(Fit, newdata = test, type = "class") 
test_error <- sum(test$Premie != pred)/nrow(test) 
test_error
```

The error did not improve.